---
title: "Activities after negative feedback initial vs sustained"
author: "Mabi Harandi"
date: "3/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(TraMineR)
library(cluster)
library(WeightedCluster)
aggnegsus <- wcAggregateCases(trajectory_data_sustained [, 5:14])
uniquenegsus <- trajectory_data_sustained[aggnegsus$aggIndex, 5:14]
negsus.seq <- seqdef(uniquenegsus, weights = aggnegsus$aggWeights)

submat.sus   <- seqsubm(negsus.seq, method= "TRATE")
dist.om1.sus <- seqdist(negsus.seq, method="OM", indel=1, sm=submat.sus) 

trajectory_data_initial <- read.csv ("results_negative_initial.csv")
trajectory_data_sustained <- read.csv ("results_negative_sustained.csv")


trajectory_data_initial.labels <- c( "community", "correct", "impressions" ,"incorrect" ,"learn",  "NonGold", "socialize", "task","viewing")
trajectory_data_initial.scodes <- c("CM", "CR", "IM" , "IC", "LR", "NG", "SO", "TA", "VI")

trajectory_data_initial.seq <- seqdef(trajectory_data_initial, 5:14, states=trajectory_data_initial.scodes, labels=trajectory_data_initial.labels, missing=NA, void="%", nr="*")

trajectory_data_sustained.labels <- c( "community", "correct", "impressions" ,"incorrect" ,"learn",  "NonGold", "socialize", "task","viewing")
trajectory_data_sustained.scodes <- c("CM", "CR", "IM" , "IC", "LR", "NG", "SO", "TA", "VI")

trajectory_data_sustained.seq <- seqdef(trajectory_data_sustained, 5:14, states=trajectory_data_sustained.scodes, labels= trajectory_data_sustained.labels, missing=NA, void="%", nr="*")

# sequence turbulences
trajectory_data.turb <- seqST(trajectory_data_initial.seq)
trajectory_data_sus.turb <- seqST(trajectory_data_sustained.seq)

#Compute the optimal matching distances using substitution costs based on transition rates observed in the data and a 1 indel cost. The resulting distance matrix is stored in the dist.om1 object.
submat   <- seqsubm(trajectory_data_initial.seq, method= "TRATE")
dist.om1 <- seqdist(trajectory_data_initial.seq, method="OM", indel=1, sm=submat) 

submat.sus   <- seqsubm(trajectory_data_sustained.seq, method= "TRATE")
dist.om1.sus <- seqdist(trajectory_data_sustained.seq, method="OM", indel=1, sm=submat.sus) 

clusterward1 <- agnes(dist.om1, diss=TRUE, method="ward")
cl1.3 <- cutree(clusterward1, k=2)
cl1.3fac <- factor(cl1.3, labels = c("Type 1", "Type 2")) 

clusterward1.sus <- agnes(dist.om1.sus, diss=TRUE, method="ward")
cl1.3.sus <- cutree(clusterward1.sus, k=2)
cl1.3fac.sus <- factor(cl1.3.sus, labels = c("Type 1", "Type 2")) 

#Create event sequences from the state sequences.
trajectory_data_initial.seqe <- seqecreate(trajectory_data_initial.seq)
fsubseq <- seqefsub(trajectory_data_initial.seqe, pmin.support = 0.05)

trajectory_data_sustained.seqe <- seqecreate(trajectory_data_sustained.seq)
fsubseq.sus <- seqefsub(trajectory_data_sustained.seqe, pmin.support = 0.05)

#Determine the most discriminating transitions between clusters and plot the frequencies by cluster of the 5 first ones.
discr <- seqecmpgroup(fsubseq, group=cl1.3fac)

discr.sus <- seqecmpgroup(fsubseq.sus, group=cl1.3fac.sus)


```

## Trajectory analysis using TraMineR



**Index plot of first 10 sequences of volunteers with initial contributions:


```{r plot1initial, echo=FALSE}
seqiplot(trajectory_data_initial.seq, withlegend=F)
seqlegend(trajectory_data_initial.seq) 


```




**Index plot of first 10 sequences of volunteers with sustained contributions:
```{r plot1sustained, echo=FALSE}


seqiplot(trajectory_data_sustained.seq, withlegend=F)
seqlegend(trajectory_data_sustained.seq)
```

**Frequency plot of 10 most frequent sequence of volunteers with initial contributions:


```{r plot2initial, echo=FALSE}
seqfplot(trajectory_data_initial.seq, pbarw=T, withlegend=F) 
seqlegend(trajectory_data_initial.seq) 

```



**Frequency plot of 10 most frequent sequence of volunteers with sustained contributions:

```{r plot2sustained, echo=FALSE}

seqfplot(trajectory_data_sustained.seq, pbarw=T, withlegend=F) 
seqlegend(trajectory_data_sustained.seq) 

```





**typology of the trajectories; A Ward hierarchical clustering of the sequences from the optimal matching distances and retrieve for each individual sequence the cluster membership of the 3 class solution.

** typology of the trajectories of volunteers with initial contributions:




```{r plot3, echo=FALSE}

seqdplot(trajectory_data_initial.seq, group=cl1.3fac)
seqlegend(trajectory_data_initial.seq)

```


** typology of the trajectories of volunteers with sustained contributions:


```{r plot3sustained, echo=FALSE}

seqdplot(trajectory_data_sustained.seq, group=cl1.3fac.sus)

seqlegend(trajectory_data_sustained.seq)

```



The 10 most frequent sequences of each cluster of volunteers with initial contributions:

```{r plot4, echo=FALSE}

seqfplot(trajectory_data_initial.seq, group=cl1.3fac, pbarw=T)
seqlegend(trajectory_data_initial.seq)

```



The 10 most frequent sequences of each cluster of volunteers with sustained contributions:

```{r plot4sustained, echo=FALSE}


seqfplot(trajectory_data_sustained.seq, group=cl1.3fac.sus, pbarw=T)
seqlegend(trajectory_data_sustained.seq)
```



**The 10 most frequent event subsequences of volunteers with initial contributions:
 ---event sequences are created from the state sequences

```{r plot5, echo=FALSE}

plot(fsubseq[1:10], col="cyan")


```




**The 10 most frequent event subsequences of volunteers with sustained contributions:
 ---event sequences are created from the state sequences

```{r plot5sustained, echo=FALSE}


plot(fsubseq.sus[1:10], col="cyan")

```

**The most discriminating transitions between clusters and plot the frequencies by cluster of the first five ones. for volunteers with initial contributions


```{r plot6, echo=FALSE}

plot(discr[1:5])



```

**The most discriminating transitions between clusters and plot the frequencies by cluster of the first five ones. For volunteers with sustained contributions


```{r plot6sustained, echo=FALSE}


plot(discr.sus[1:5])

```